---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# eruptR

<!-- badges: start -->
<!-- badges: end -->

The goal of eruptR is to analyse and comprehend volcanic explosivity trends. Users can use this function to query the dataset using volcano names and receive data linked to the Volcano Explosivity Index (VEI). The dataset includes not only the categorising and features of these volcanoes but also detailed information regarding their eruptions across time. 

There are a number of functions included in the package that can help answer questions such as:

- How to generate a Fibonacci series of a given input?
- What does the Volcanic Explosivity Index (VEI) indicate for a particular volcano during a specific year?
- What is the highest Volcanic Explosivity index of the top volcanoes for that input year?
- The package also includes a method that executes a shiny application designed to assess various elements of the data.


## Installation

You can install the development version of eruptR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ETC5523-2023/rpkg-akanksha03042001")
```

This command is used to load the package library -

```{r}
library(eruptR)
```

## Example

- **fibonacci_sequence** - When given a specific number as input, the numerical function displays the Fibonacci series up to that particular input number.

```{r example-1, eval=TRUE}
fibonacci_series(10)
```

- **explosive_index** - A function that takes a year as input and returns the name of the volcano as well as the maximum recorded Volcanic Explosivity Index (VEI) for that year.

```{r example-2, eval=TRUE, message=FALSE, warning=FALSE}
explosive_index(2011)
```

- **volcanic_eruption_counts** - A parameterized R Shiny function that takes in a year and creates a figure demonstrating the relationship between Volcanic Explosivity Index (VEI) and volcano names.

```{r example-3, eval=TRUE}
volcanic_eruption_counts(2001)
```

- **Launching Shiny App** - A function which launches a R-shiny app from the package.

```{r shiny, eval=FALSE}
run_app()
```

The link of the package can be found [here](https://github.com/ETC5523-2023/rpkg-akanksha03042001.git). 
dev
